---
title: "Permutation subset"
output:
  pdf_document: default
  html_notebook: default
---


```{r}
library("data.table")
library("trio")
source("Weinberg_optimised.R")
set.seed(123)
```


No need to run this. It is how I made the subset of 10 families and 1000 variants
```{r eval=FALSE}
# Sample families
fam <- fread("sorted_trios_QC.fam")
samples_fam <- sample(unique(fam$V1),10)
fwrite(fam[V1 %in% samples_fam, 1:2], file = "subset_fam.txt", row.names = FALSE, col.names = FALSE, sep = "\t")
```

```{r eval=FALSE}
# Sample variants
bim <- fread("sorted_trios_QC.bim")
samples_bim <- as.data.table(sample(unique(bim$V2),1000))
fwrite(samples_bim, file = "subset_bim.txt", row.names = FALSE, col.names = FALSE, sep = "\t")
```

In PLINK plink --bfile sorted_trios_QC --keep subset_fam.txt --extract subset_bim.txt --recode --out test_subset

The code for original data and permuted data.
```{r}
PO <- 1999
R <- 10
W <- 0.42^2

ped <- read.pedfile("/home/kim/Documents/UCD/R/SPARK_data/Debugging/subset_with_sig.ped", first.row = TRUE, coded = "ATCG", naVal = 0, cols4ID = TRUE)

## Original data
  geno_original <- ped2geno(ped, coded = "ATCG") # too small sample
  
  # Estimating maternal effects
  maternal_original <- WeinbergLRT_op(geno_original, model = "general", maternal = T,  child = F)
  
  
  maternal_original[, Z := estS1/ seS1]
  
  maternal_original[, BF :=  sqrt(seS1^2 + W / seS1^2) * exp((-Z^2/2)*(W/(seS1^2 + W)))]
  ped_original <- ped

## One permutation:

  ped <- as.data.table(ped)
  no_trios <- length(unique(ped$famid))
  
  # Coin that decides to change the lable or not
  set.seed(123)
  coin <- sample(1:2, no_trios, replace = TRUE)
  
  # Father = 1, mother = 2
  # If coin changed to 2 --> father becomes mother, and mother becomes father
  for (i in 1:length(coin)) {
    ped[(1+i*3-3), sex := coin[i]] 
    ped[(2+i*3-3), sex := ifelse(coin[i] == 1, 2,1) ]
  }
  # permutated ped used in analysis
  new_ped <- ped[order(famid, fatid, motid, sex)]
  geno_perm <- ped2geno(new_ped, coded = "ATCG")
  
  # Estimating maternal effects
  maternal_perm <- WeinbergLRT_op(geno_perm, model = "general", maternal = T,  child = F)
  
  
  maternal_perm[, Z := estS1/ seS1]
  maternal_perm[, BF :=  sqrt(seS1^2 + W / seS1^2) * exp((-Z^2/2)*(W/(seS1^2 + W)))]


# All are same except this 4
 index <- which(round(maternal_perm$BF, digits = 6) != round(maternal_original$BF, digit = 6))
 index
```


Out of 829 variants, 6 have different BF, the rest have the same.
When we compare them, only BF for three variant is higher than the BF from the original dataset, the rest are the same or lower (making our finding unrelevant).
```{r}
maternal_original[index, c("SNP", "BF")] 
```

```{r}
maternal_perm[index, c("SNP", "BF")]
```

```{r}
coin # 4, 6, 7 and 8 famid should have switched parents
```

Compare original dataset and created permuted dataset
```{r}
ped_original[c(10:12, 16:22),c(1:5,13:14,19:24 )]
```

```{r}
new_ped[c(10:12, 16:22),c(1:6,13:14,19:24)]
```

